Final Workflow for CLM5 paper

### 2019-05-28 workflow2.tex
Updates from ShareLaTeX
Updates from Overleaf

\section{Spin-up}
\subsection{Make 1850 spin-up default runs from scratch}
Make single point case from scratch for each site by running this script (based on Charlie's FATES version) 'n' times once for each site (that could be improved on!)..:\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/fromscratch_CTSM_make_site_spinup_case_defaults}}}\\

>>>>

\section{Spin-up}

\subsection{Make base Case}
/gpfs/fs1/work/rfisher/git/clm5.0_may19/cime/scripts/CLM5_POINTSIMS/CLM5.0_may19_basebuild
Using the /gpfs/fs1/work/rfisher/git/clm5.0_may19/cime/scripts/CLM5_POINTSIMS/CLM5.0_may19_basebuild

\subsection{Make 1850 spin-up default runs from scratch}
Make single point case from scratch for each site by running this script (based on Charlie's FATES version) 'n' times once for each site (that could be improved on!)..:\\
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/fromscratch_CTSM_make_site_spinup_case_defaults}}}\\

\subsection{Make spinup ensemble}
/glade/work/rfisher/git/CLM5_FACE_EXPTS/case_scripts
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_spinup_mic_ensembles
}}}\\
